Forecasting the 2024 U.S. Presidential Election

### 2024-11-04 paper/paper.qmd
Modify Measurement part

The goal of measurement is to distill individual voter opinions into a reliable estimate of Electoral College outcomes, transforming raw polling data into a clear forecast of each candidate’s support.

To capture public sentiment, surveys ask questions like, “If the election were held today, who would you vote for?” Responses are summarized by pollsters as a percentage of support for each candidate, creating a structured outcome variable that reflects aggregate support.

- Data Source and Quality Assurance: The dataset is sourced from @fivethirty, a trusted platform recognized for its stringent standards in polling data qualityOnly high-quality polls are included to ensure broad representation of likely U.S. voters. Each poll includes essential details, such as pollster identity, survey dates, sample size, and methodology, all documented in the dataset. While these standards effectively capture respondents' voting intentions, they are based on historical benchmarks that may not fully account for recent methodological shifts or emerging biases. Additionally, the dataset provides a numeric grade, transparency score, and pollster rating, calculated by @fivethirty using their internal criteria and scoring mechanisms. 
- Temporal Limitations and Data Recency: Polling data captures discrete snapshots of voter sentiment rather than continuous updates. Consequently, the analysis reflects voter intentions only at specific moments, which may not capture rapid opinion shifts, particularly as Election Day approaches. To mitigate this limitation, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure that the data remains reflective of current voter sentiment.
- Participation and Response Bias: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid. Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to be more socially acceptable) can affect data accuracy. These biases may introduce discrepancies between expressed opinions and actual voting behavior, potentially influencing forecast reliability.
- Regional Sampling Imbalances: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which might skew state-level and, by extension, national forecasts. Such discrepancies highlight the challenge of producing a uniformly accurate forecast across all regions.

>>>>

The goal of measurement is to distill individual voter opinions into a reliable estimate of Electoral College outcomes, transforming raw polling data into a forecast of each candidate’s support.

To capture public sentiment, surveys ask questions like, “If the election were held today, who would you vote for?” Pollsters summarize responses as percentages of support for each candidate, creating a structured outcome variable that reflects aggregate support.

- **Data Source and Quality Assurance**: The dataset is sourced from @fivethirty, a trusted platform recognized for its high standards in polling data quality. Only polls that meet specific criteria are included to ensure broad representation of likely U.S. Each poll documents essential details, including the pollster's identity, survey dates, sample size, and methodology. While these standards effectively capture respondents' voting intentions, they are based on historical benchmarks that may not fully adjust for recent changes in polling methods. The dataset also provides a numeric grade, transparency score, and pollster rating, calculated by @fivethirty using their internal criteria.
- **Temporal Limitations and Data Recency**: Polling data captures discrete snapshots of voter sentiment rather than continuous updates. Consequently, the analysis reflects intentions at particular times, which may not account for rapid shifts in opinion closer to Election Day. To address this, recency adjustments are applied to account for the time elapsed since each poll was conducted, helping to ensure the data remains reflective of current voter sentiment.
- **Participation and Response Bias**: Despite the rigorous methodology, certain biases in survey participation are difficult to avoid. Self-selection bias (where individuals choose whether to participate) and social desirability bias (where respondents may adjust their responses to appear socially acceptable) can affect data accuracy. These biases may introduce discrepancies between expressed opinions and actual voting behavior, potentially influencing forecast reliability.
- **Regional Sampling Imbalances**: The frequency of polling varies significantly by state, with battleground states receiving more frequent attention than states considered “safe.” This uneven distribution can lead to imbalances in regional representation, which may skew state-level and national forecasts. Such discrepancies highlight the challenge of producing a uniformly accurate forecast across all regions.
